Machine Learning Approaches for Ammonia Volatilization Prediction after Manure Application

### 2024-07-02 manuscript.qmd
renaming figures with number, and other minor changes

```{r, fig.width = 10, fig.height = 8}
plot_data_description = data_alfam2 %>%

@@

plot_data_description
```

```{r, include = FALSE}
png (file = "figures/data_description_relative_cumul.png", width = 1000, height = 700)
plot_data_description
dev.off()
```

@@

```{r, include = FALSE}
png (file = "figures/plot_residuals_complete_dataset.png", width = 1000, height = 1100)
plot_residuals_complete_dataset
dev.off()

png (file = "figures/plot_residuals_evaluation_subset.png", width = 1000, height = 1100)
plot_residuals_evaluation_subset
dev.off()
```

@@

```{r, fig.width = 10, fig.height = 8}
plot_observed_vs_predicted_values = predictions_of_all_methods %>%

@@

plot_observed_vs_predicted_values
```

```{r, include = FALSE}
png (file = "figures/observed_vs_predicted_values.png", width = 1000, height = 700)
plot_observed_vs_predicted_values
dev.off()
```

@@

```{r, fig.width = 16, fig.height = 5}
# Evaluation on evalutation subset
df_plot = df_evaluation_metrics %>%
    filter (response == "72h cum. emission") %>%
    select (- MSE, - RMSE) %>%
    filter (dataset == "Evaluation subset") %>%
    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE")))

suppressWarnings(ggplot (df_plot) +
    geom_histogram (aes (x = name, y = value, fill = method), position = "dodge", stat = "identity") +
    facet_wrap (~ name, scales = "free", nrow = 1) + 
    xlab ("") + ylab ("") + labs (fill = "") +
    theme (legend.position = "none ", 
           strip.text.y = element_text(angle = 0), 
           axis.text.x = element_blank(), 
           axis.ticks.x = element_blank(),
           strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0))) +
    scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
    ggtitle ("Evaluation subset") + theme (plot.title = element_text (margin= ggplot2::margin(0,0,20,0), hjust = 0, size = 30)))
```

```{r, fig.width = 16, fig.height = 5}
# Evaluation on calibration subset
df_plot = df_evaluation_metrics %>%
    filter (response == "72h cum. emission") %>%
    select (- MSE, - RMSE) %>%
    filter (dataset == "Calibration subset") %>%
    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE")))

suppressWarnings(ggplot (df_plot) +
    geom_histogram (aes (x = name, y = value, fill = method), position = "dodge", stat = "identity") +
    facet_wrap (~ name, scales = "free", nrow = 1) + 
    xlab ("") + ylab ("") + labs (fill = "") +
    theme (legend.position = "bottom", 
           strip.text.y = element_text(angle = 0), 
           axis.text.x = element_blank(), 
           axis.ticks.x = element_blank(),
           strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0))) +
    scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
    ggtitle ("Calibration subset") + theme (plot.title = element_text (margin= ggplot2::margin(0,0,20,0), hjust = 0, size = 30)))
```

@@

```{r, fig.width = 10, fig.height = 10}
plot_scenario_predictions = data_scenarios %>% 
    select (app.mthd, incorp, t.incorp, man.ph,
            efficacy_random_forest, efficacy_xgboost, efficacy_lasso, efficacy_alfam2) %>%

@@

plot_scenario_predictions
```

```{r, include = FALSE}
png (file = "figures/emissions_for_scenarios.png", width = 1000, height = 800)
plot_scenario_predictions
dev.off()
```

@@

plot = ggplot (data_tmp) +
    geom_histogram (aes (efficacy_xgboost)) +
    facet_wrap (~ tan.app + app.rate + group_rain) +
    xlab ("Efficacy") +
    ylab ("Number of predictions") +
    theme (axis.title.y = element_text (margin = ggplot2::margin (r = 20), size = 18),
           strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)),
           strip.text = element_text (size = 18),
           axis.text = element_text (size = 18),
           axis.title.x = element_text (size = 18))

plot
```

```{r, include = FALSE}
png (file = "figures/Xgboost_positive_predictions_plot.png", width = 1200, height = 800)
plot
dev.off()
```

@@

png (file = "figures/plot_shap.png", width = 1000, height = 900)
do.call ("grid.arrange", 
         c (list(plot_shap_rf_2, 
                 plot_shap_xgboost_2, 
                 legend), 
            list(layout_matrix = as.matrix(c (1, 2, 3)),
                  heights = c (0.8, 1, 0.2))))
dev.off()
```

```{r}
png (file = "figures/plot_importance.png", width = 1300, height = 800)
grid.arrange (plot_importance_rf, plot_importance_xgboost, nrow = 1)
dev.off()
```

@@

@@

```{r, fig.height = 8, fig.width = 10}
plot_temperature_comparison = rbind (
    data %>% select (temp = Tem) %>% mutate (data = "Data from Peng Xu et al (2024)"),
    data_alfam2 %>% select (temp = air.temp) %>% mutate (data = "Data used for the alfam2 model")
) %>%

@@

plot_temperature_comparison
```

```{r, include = FALSE}
png (file = "figures/plot_temperature_comparison.png", width = 1000, height = 600)
plot_temperature_comparison
dev.off()
```

>>>>

```{r, fig.width = 10, fig.height = 8}
Figure_1 = data_alfam2 %>%

@@

Figure_1
```

```{r, include = FALSE}
tiff (file = "figures/Figure_1.tiff", width = 1000, height = 700)
Figure_1
dev.off()
```

@@

```{r, include = FALSE}
tiff (file = "figures/Figure_10.tiff", width = 1000, height = 1100)
plot_residuals_complete_dataset
dev.off()

tiff (file = "figures/Figure_11.tiff", width = 1000, height = 1100)
plot_residuals_evaluation_subset
dev.off()
```

@@

```{r, fig.width = 10, fig.height = 8}
Figure_2 = predictions_of_all_methods %>%

@@

Figure_2
```

```{r, include = FALSE}
tiff (file = "figures/Figure_2.tiff", width = 1000, height = 700)
Figure_2
dev.off()
```

@@

```{r, fig.width = 16, fig.height = 5}
# Evaluation on evalutation subset
df_plot_eval = df_evaluation_metrics %>%
    filter (response == "72h cum. emission") %>%
    mutate (method = recode (method, "alfam2" = "ALFAM2", "xgboost" = "Gradient boosting", "random forest" = "Random forest", "lasso" = "Lasso")) %>%
    mutate (method = factor (method, levels = c ("ALFAM2", "Lasso", "Random forest", "Gradient boosting"))) %>%
    select (- MSE, - RMSE) %>%
    filter (dataset == "Evaluation subset") %>%
    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE")))

plot_eval = suppressWarnings(ggplot (df_plot_eval) +
    geom_histogram (aes (x = name, y = value, fill = method), position = "dodge", stat = "identity") +
    facet_wrap (~ name, scales = "free", nrow = 1) + 
    xlab ("") + ylab ("") + labs (fill = "") +
    theme (legend.position = "none ", 
           strip.text.y = element_text(angle = 0), 
           axis.text.x = element_blank(), 
           axis.text.y = element_text (size = 18),
           axis.ticks.x = element_blank(),
           strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0), size = 24)) +
    scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
    ggtitle ("Evaluation subset") + theme (plot.title = element_text (margin= ggplot2::margin(0,0,20,0), hjust = 0, size = 26)))

plot_eval
```

```{r, include = FALSE}
tiff (file = "figures/plot_eval.tiff", width = 1000, height = 320)
plot_eval
dev.off()
```

```{r, fig.width = 16, fig.height = 5}
# Evaluation on calibration subset
df_plot_calib = df_evaluation_metrics %>%
    filter (response == "72h cum. emission") %>%
    mutate (method = recode (method, "alfam2" = "ALFAM2", "xgboost" = "Gradient boosting", "random forest" = "Random forest", "lasso" = "Lasso")) %>%
    mutate (method = factor (method, levels = c ("ALFAM2", "Lasso", "Random forest", "Gradient boosting"))) %>%
    select (- MSE, - RMSE) %>%
    filter (dataset == "Calibration subset") %>%
    pivot_longer (cols = c (Pearsons_r, ME, MAE, MBE)) %>%
    mutate (name = factor (name, levels = c("Pearsons_r", "ME", "MAE", "MBE")))

plot_calib = suppressWarnings(ggplot (df_plot_calib) +
    geom_histogram (aes (x = name, y = value, fill = method), position = "dodge", stat = "identity") +
    facet_wrap (~ name, scales = "free", nrow = 1) + 
    xlab ("") + ylab ("") + labs (fill = "") +
    theme (legend.position = "bottom", 
           strip.text.y = element_text(angle = 0), 
           axis.text.x = element_blank(), 
           axis.text.y = element_text (size = 18),
           axis.ticks.x = element_blank(),
           strip.text.x = element_text (margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0), size = 24),
           axis.title.x = element_text (margin = ggplot2::margin (b = - 10))) +
    scale_fill_manual (values = Dark2[c(2, 5, 6, 8)]) +
    ggtitle ("Calibration subset") + theme (plot.title = element_text (margin= ggplot2::margin(0,0,20,0), hjust = 0, size = 26)))

plot_calib
```

```{r, include = FALSE}
tiff (file = "figures/plot_calib.tiff", width = 1000, height = 350)
plot_calib
dev.off()
```

@@

```{r, fig.width = 10, fig.height = 10}
Figure_6 = data_scenarios %>% 
    select (app.mthd, incorp, t.incorp, man.ph,
            efficacy_random_forest, efficacy_xgboost, efficacy_lasso, efficacy_alfam2) %>%

@@

Figure_6
```

```{r, include = FALSE}
tiff (file = "figures/Figure_6.tiff", width = 1000, height = 800)
Figure_6
dev.off()
```

@@

Figure_8 = ggplot (data_tmp) +
    geom_histogram (aes (efficacy_xgboost)) +
    facet_wrap (~ tan.app + app.rate + group_rain) +
    xlab ("Efficacy") +
    ylab ("Number of predictions") +
    theme (axis.title.y = element_text (margin = ggplot2::margin (r = 20), size = 18),
           strip.text.x = element_text(margin = ggplot2::margin(t = 8, b = 8, r = 0, l = 0)),
           strip.text = element_text (size = 18),
           axis.text = element_text (size = 18),
           axis.title.x = element_text (size = 18))

Figure_8
```

```{r, include = FALSE}
tiff (file = "figures/Figure_8.tiff", width = 1200, height = 800)
Figure_8
dev.off()
```

@@

tiff (file = "figures/Figure_5.tiff", width = 1000, height = 900)
do.call ("grid.arrange", 
         c (list(plot_shap_rf_2, 
                 plot_shap_xgboost_2, 
                 legend), 
            list(layout_matrix = as.matrix(c (1, 2, 3)),
                  heights = c (0.8, 1, 0.2))))
dev.off()
```

```{r}
tiff (file = "figures/Figure_4.tiff", width = 1300, height = 800)
grid.arrange (plot_importance_rf, plot_importance_xgboost, nrow = 1)
dev.off()
```

@@

```{r, fig.height = 5, fig.width = 7}
Figure_7 = data_alfam2 %>%
    ggplot () +
        geom_point (aes (x = man.ph, y = tan.app, color = man.source), size = 5) +
        scale_color_manual (values = Dark2) +
        xlab ("pH") +
        ylab ("TAN") +
        theme (legend.position = "bottom") +
        labs (color = "Manure source") +
        NULL

Figure_7
```

```{r, include = FALSE}
tiff (file = "figures/Figure_7.tiff", width = 1200, height = 800)
Figure_7
dev.off()
```

@@

```{r, fig.height = 8, fig.width = 10}
Figure_9 = rbind (
    data %>% select (temp = Tem) %>% mutate (data = "Data from Peng Xu et al (2024)"),
    data_alfam2 %>% select (temp = air.temp) %>% mutate (data = "Data used for the alfam2 model")
) %>%

@@

Figure_9
```

```{r, include = FALSE}
tiff (file = "figures/Figure_9.tiff", width = 1000, height = 600)
Figure_9
dev.off()
```
